\documentclass[11pt]{article}
\usepackage[
  letterpaper,
  top=0.5in,
  bottom=0.5in,
  left=0.5in,
  right=0.5in
]{geometry}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\raggedright
\pagestyle{empty}

\input{glyphtounicode}
\pdfgentounicode=1

\titleformat{\section}{\bfseries\large}{}{}{}[\titlerule\vspace{-4pt}]

\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-1pt, leftmargin=12pt, topsep=7pt}

\begin{document}

\centerline{\Huge Jane Doe}
\centerline{\Large Full-Stack Software Engineer}
\vspace{4pt}
\centerline{
  \href{mailto:jane.doe@email.com}{jane.doe@email.com} | \href{tel:+15551234567}{+1-555-123-4567} | \href{https://www.linkedin.com/in/janedoe}{linkedin.com/in/janedoe} | \href{https://github.com/janedoe}{github.com/janedoe}
}

\section*{Summary}

\begin{itemize}
  \item Full-stack engineer with \textbf{4 years} of experience building web applications and backend services. \\
  \item Proficient in \textbf{Python, JavaScript, React, and Node.js} with hands-on experience deploying to \textbf{AWS}. \\
  \item Familiar with \textbf{CI/CD pipelines, Docker, and PostgreSQL}. \\
\end{itemize}

\section*{Skills}

\begin{itemize}
  \item \textbf{Languages}: Python, JavaScript, TypeScript, SQL \\
  \item \textbf{Frontend}: React, HTML, CSS, Tailwind CSS \\
  \item \textbf{Backend}: Node.js, Express, Django, Flask \\
  \item \textbf{Databases}: PostgreSQL, MongoDB, Redis \\
  \item \textbf{DevOps}: Docker, AWS (EC2, S3, RDS), GitHub Actions \\
  \item \textbf{Tools}: Git, Jira, Figma \\
\end{itemize}

\section*{Experience}

\textbf{Acme Corp} \\
\textbf{Software Engineer} \hfill March 2022 -- Present \\

\begin{itemize}
  \item Built and maintained a customer-facing dashboard using \textbf{React and TypeScript}, serving 10,000+ daily active users. \\
  \item Developed RESTful APIs with \textbf{Django} and \textbf{PostgreSQL} to support product features and third-party integrations. \\
  \item Set up \textbf{CI/CD pipelines} with GitHub Actions, reducing deployment time from 30 minutes to 8 minutes. \\
  \item Collaborated with product and design teams in an Agile environment to ship features on a 2-week sprint cycle. \\
\end{itemize}

\textbf{StartupXYZ} \\
\textbf{Junior Developer} \hfill June 2020 -- February 2022 \\

\begin{itemize}
  \item Built internal tools using \textbf{Flask} and \textbf{jQuery} to streamline operations for a 50-person team. \\
  \item Wrote unit and integration tests, increasing code coverage from 40\% to 85\%. \\
  \item Managed deployments to \textbf{AWS EC2} and configured \textbf{S3} for static asset hosting. \\
\end{itemize}

\section*{Projects}

\textbf{TaskFlow -- Project Management App} \hfill \href{https://github.com/janedoe/taskflow}{\underline{github.com/janedoe/taskflow}} \\

\begin{itemize}
  \item Built a Kanban-style project management app with \textbf{React, Node.js, and MongoDB}. \\
  \item Implemented real-time updates using WebSockets and drag-and-drop UI with React DnD. \\
\end{itemize}

\section*{Education}

\textbf{University of California, Berkeley} -- BS in Computer Science \hfill May 2020 \\

\end{document}
